\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}
\usepackage{multicol}
\usepackage{xcolor}

% personal data
% optional, remove / comment the lines if not wanted
\name{Christopher}{Hann-Soden}
\address{213 Hillside Ave, Piedmont, CA, 94611}{}{} % the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{(925)872-2716}
\email{channsoden@gmail.com}
\homepage{https://github.com/channsoden}

% Use this command for multiple degrees/positions within a university/company
\newcommand*{\cvsimple}[4][.25em]{
  \begin{tabular*}{\maincolumnwidth}{l@{\extracolsep{\fill}}r}%
    % {\bfseries #4} & {\bfseries #5}\\%
    {\itshape #3} & {\itshape #2}\\%
  \end{tabular*}%
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\textbf{Computational Biologist and Bioinformatician}

I earned my PhD for developing statistical and machine learning algorithms to compare genomes. I'm interested in developing algorithms and pipelines to solve hard problems.

%\vspace{12pt}

\section{Experience}
\begin{itemize}
  
\vspace{5pt}
\item{\cventry{Jan 2018--Present}{Domain Consultant}{UC Berkeley}{Berkeley, CA}{Berkeley Research Computing}{\begin{itemize}
    \vspace{3pt}
    \item[]{\textit{Key Skills}: communication, HPC, Unix systems, Git, cloud computing, collaboration.}
    \vspace{3pt}
    \item{Provided technical support and consulting services to researchers in data-driven domains.}
    \item{Developed training and documentation for campus IT services and infrastructure, including HPC and cloud services.}
  \end{itemize}}}
  
\vspace{5pt}
\item{\cventry{Jul 2012--Dec 2018}{Graduate Student Researcher}{UC Berkeley}{Berkeley, CA}{Taylor Lab}{\begin{itemize}
    \vspace{3pt}
    \item[]{\textit{Key Skills}: NGS, phylogenetics, genomics, population genetics, Python, R, HPC, writing, oral presentation.}
    \vspace{3pt}
    \item{Independently developed a statistical framework and efficient algorithm for measuring genomic rearrangement rates.}
    \item{Used statistical and machine learning methods of population and comparative genomics to investigate the evolutionary consequences of breeding system transitions in \textit{Neurospora}. }
    \item{Modeled the transcriptional response of \textit{Neurospora} to acclimation and adaptation to warmer temperatures.}
    \item{Administered and maintained the laboratory's Linux server.}
  \end{itemize}}}

\vspace{5pt}
\item{\cventry{2014--2018}{Instructor}{UC Berkeley}{Berkeley, CA}{}{\begin{itemize}
    \vspace{3pt}
    \item[]{\textit{Key Skills}: oral presentation, information synthesis, communication, teamwork.}
    \vspace{3pt}
    \item{Introduction to Programming for Bioinformatics (Summers 2014-2017, Winters 2016-2018)}
    \item{General Biology (Spring 2015, Spring 2018)}
    \item{Microbiology Laboratory (Spring 2014)}
  \end{itemize}}}
  
\vspace{5pt}
\item{\cventry{Aug 2011--May 2012}{Laboratory Assistant I}{UC Berkeley}{Berkeley, CA}{Glaunsinger Lab}{\begin{itemize}
    \vspace{3pt}
    \item[]{\textit{Key Skills}: molecular biology, cell culture, time management, neatness, organization, teamwork.}
    \vspace{3pt}
    \item{Systematically mapped interactions between human and viral proteins.}
    \item{Developed and implemented work flows for cloning, heterologous gene expression, coimmunoprecipitation, and blotting.}  
  \end{itemize}}}
  
%\vspace{5pt}
  %\item{\cventry{2008--2010}{Undergraduate Student}{Humboldt State University}{Arcata, CA}{}{\vspace{3pt}Research: Investigating the visual capabilities of the purple sea urchin. Specialization in biophysics and behavioral ecology.}}

%\vspace{5pt}
%\item{\cventry{2013--2015}{Mentor}{Oakland Science and Math Outreach}{Oakland, CA}{}{\begin{itemize}
%    \item{Tutoring high school math \& science.}
%    \item{Providing guidance and developing life skills.}
%    \item{Key Skills: communication, compassion, personal engagement.}
%\end{itemize}}}
  
%\vspace{5pt}
%\item{\cventry{2009--2010}{Genetics}{Tutor}{Humboldt State University}{}{}}

\end{itemize}

\pagebreak

\section{Education}
\begin{itemize}

\vspace{5pt}
\item{\cventry{2012--2018}{Microbiology}{UC Berkeley}{Berkeley, CA}{Doctorate of Philosophy}{}}
\item[]{\cvsimple{2015--2017}{Philomathia Scholars Graduate Fellowship}{}}
\item[]{\cvsimple{2016}{Webmaster, Microbiology Student Group}{}}
\item[]{\cvsimple{2015}{Symposium Chair, Microbiology Student Group}{}}
  
\vspace{5pt}
\item{\cventry{2008--2010}{Biology \& Zoology}{Humboldt State University}{Arcata, CA}{Bachelor of Science}{\textit{cum laude}}}

\end{itemize}

% Publications list
\nocite{*} % show all publications without needing to cite them
\bibliographystyle{unsrt}
{\small \bibliography{publications} } % 'publications' is the name of a BibTeX file

\section{Other Skills \& Projects}

\begin{multicols}{3}

  \textbf{Dancify} - A web app to tag and visually explore your music using Spotify data.
  \newline
  \newline
  
  \textbf{Cryptyx} - A free and open source block chain ticketing protocol and web service.
  \newline
  \newline
  
  \textbf{Martial Arts} - Shorinji Kempo, 12 years.
  \newline
  \textbf{Partner Dancing} - Blues \& fusion, 5 years.

\end{multicols}

% Include synonyms to keywords for dumb robots.
\textcolor{white}{\tiny \textsuperscript{analyze data analysis visualization genetics algorithms statistics unsupervised learning markov models classification data mining bioinformatics informatics biostatistics computational biology datasets} }

\textcolor{white}{\tiny \textsuperscript{computer science version control written communication skills interpersonal skills verbal communication skills collaborate collaborative project independent project driven} }

\end{document}


